### 2013-07-15 tests_Auto-Mpg.Rmd
beginning latex section of Results

sapply(my.data, class)
my.data$x3 <- as.numeric(my.data$x3) # x3 was a factor, make it a numeric value
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50)

@@

write.table(df, "")

@@

########################################################
# Lambda Test
lambda.values <- seq(0.5,0.999,length.out=20)
n.runs <- 5

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=50, iterations=25)

>>>>

sapply(my.data, class)
my.data$x3 <- as.numeric(my.data$x3) # x3 was a factor, make it a numeric value
my.data <- as.data.frame(scale(my.data)) # scale it
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50, lambda=0.8)

@@

@@

########################################################
# Lambda Test
lambda.values <- seq(0.7,1.3,by=0.05)
n.runs <- 10

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=60, iterations=60)

### 2013-07-15 tests_Housing.Rmd
beginning latex section of Results

sapply(my.data, class)
# my.data$x3 <- as.numeric(my.data$x3) # x3 was a factor, make it a numeric value
head(my.data,8)

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50)

@@

save(report, file="Housing300.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300.txt")

>>>>

sapply(my.data, class)
# my.data$x3 <- as.numeric(my.data$x3) # x3 was a factor, make it a numeric value
head(my.data,8)
my.data <- as.data.frame(scale(my.data))

@@

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=100, lambda=0.8, runs=25)

@@

save(report, file="Housing300_lambda0.8.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.8.txt")

### 2013-07-15 tests_test.Rmd
beginning latex section of Results

source("gapolyfuncs.R")
report <- make.report(my.data, population=50, iterations=25, mutation.rate=0.05, runs=1)

@@

# Lambda Test
lambda.values <- seq(1,2,length.out=20)
n.runs <- 1

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=100, iterations=50, mutation.rate=0.05)

@@

# Lambda Test
lambda.values <- seq(0.5,2,length.out=20)
n.runs <- 1
